Discovering the Rules of language using Bayesian Program Learning

### 2018-04-30 test.tex
updated problem solutions

>>>>

\emph{Standard Ukrainian:}\\\begin{longtable}{llllllllll|l}\toprule
$\varnothing$ $+$stem$+$ $\varnothing$ & $\varnothing$ $+$stem$+$ \textipa{am} & $\varnothing$ $+$stem$+$ \textipa{ov\super ji} & $\varnothing$ $+$stem$+$ \textipa{i} & $\varnothing$ $+$stem$+$ \textipa{ov\super ji} & $\varnothing$ $+$stem$+$ \textipa{o} & $\varnothing$ $+$stem$+$ \textipa{a} & $\varnothing$ $+$stem$+$ \textipa{u} & $\varnothing$ $+$stem$+$ \textipa{i} & $\varnothing$ $+$stem$+$ $\varnothing$ & UR
\textipa{zub} & \textipa{zubam} & \textipa{zubov\super ji} & \textipa{zub\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{sv\super jit} & \textipa{sv\super jitam} & \textipa{sv\super jitov\super ji} & \textipa{sv\super jit\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{z\super jat\super j} & \textipa{z\super jat\super jam} & \textipa{z\super jatev\super ji} &  --  & \textipa{z\super jatev\super ji} &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{koS\super jil\super j} & \textipa{koSel\super jam} & \textipa{koSelev\super ji} & \textipa{koSel\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{zlod\super jij} & \textipa{zlod\super jijam} & \textipa{zlod\super jijev\super ji} &  --  & \textipa{zlod\super jijev\super ji} &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{m\super jis\super jar\super s \super j} & \textipa{m\super jis\super jar\super s \super jam} & \textipa{m\super jis\super jat\super sev\super ji} & \textipa{m\super jis\super jar\super s \super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{korovaj} & \textipa{korovajam} & \textipa{korovajev\super ji} & \textipa{korovaji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{kam\super jin\super j} & \textipa{kamen\super jam} & \textipa{kamenev\super ji} & \textipa{kamen\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{m\super jid\super j} & \textipa{m\super jid\super jam} & \textipa{m\super jidev\super ji} & \textipa{m\super jid\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{xl\super jiw} & \textipa{xl\super jivam} & \textipa{xl\super jivov\super ji} & \textipa{xl\super jiv\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{holub} & \textipa{holubam} & \textipa{holubov\super ji} & \textipa{holub\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{s\super jin} & \textipa{s\super jinam} & \textipa{s\super jinov\super ji} & \textipa{s\super jin\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{leb\super jid\super j} & \textipa{lebed\super jam} & \textipa{lebedev\super ji} & \textipa{lebed\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{sus\super jid} & \textipa{sus\super jidam} & \textipa{sus\super jidov\super ji} &  --  & \textipa{sus\super jidov\super ji} &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{t\super Solov\super jik} & \textipa{t\super Solov\super jikam} & \textipa{t\super Solov\super jikov\super ji} &  --  & \textipa{t\super Solov\super jikov\super ji} &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{l\super jid} & \textipa{ledam} & \textipa{ledov\super ji} & \textipa{led\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{bil\super j} & \textipa{bol\super jam} & \textipa{bolev\super ji} & \textipa{bol\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{riw} & \textipa{rovam} & \textipa{rovov\super ji} & \textipa{rov\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{stiw} & \textipa{stolam} & \textipa{stolov\super ji} & \textipa{stol\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{d\super jid} & \textipa{d\super jidam} & \textipa{d\super jidov\super ji} &  --  & \textipa{d\super jidov\super ji} &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{l\super jit} & \textipa{l\super jotam} & \textipa{l\super jotov\super ji} & \textipa{l\super jot\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{mist} & \textipa{mostam} & \textipa{mostov\super ji} & \textipa{most\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
\textipa{vet\super Sir} & \textipa{vet\super Soram} & \textipa{vet\super Sorov\super ji} & \textipa{vet\super Sor\super ji} &  --  &  --  &  --  &  --  &  --  &  --  &  -- \\
 --  &  --  &  --  &  --  &  --  & \textipa{t\super jilo} & \textipa{t\super jila} & \textipa{t\super jilu} & \textipa{t\super jil\super ji} & \textipa{t\super jiw} &  -- \\
 --  &  --  &  --  &  --  &  --  & \textipa{koleso} & \textipa{kolesa} & \textipa{kolesu} & \textipa{koles\super ji} & \textipa{kol\super jis} &  -- \\
 --  &  --  &  --  &  --  &  --  & \textipa{ozero} & \textipa{ozera} & \textipa{ozeru} & \textipa{ozer\super ji} & \textipa{oz\super jir} &  -- \\
 --  &  --  &  --  &  --  &  --  & \textipa{selo} & \textipa{sela} & \textipa{selu} & \textipa{sel\super ji} & \textipa{s\super jiw} &  -- \\
 --  &  --  &  --  &  --  &  --  & \textipa{pole} & \textipa{pol\super ja} & \textipa{pol\super ju} & \textipa{pol\super ji} & \textipa{pil\super j} &  -- \\
 --  &  --  &  --  &  --  &  --  & \textipa{slovo} & \textipa{slova} & \textipa{slovu} & \textipa{slov\super ji} & \textipa{sliw} &  -- \\
 --  &  --  &  --  &  --  &  --  & \textipa{more} & \textipa{mor\super ja} & \textipa{mor\super ju} & \textipa{mor\super ji} & \textipa{mir\super j} &  -- \\
\verb|[ ]| $\to$ $-2$ / \verb|[ ]| \verb|[ ]| \verb|_| \verb|[+sibilant]| \#\\\verb|[ ]| $\to$ \textipa{e} / \verb|[+palletized]| \verb|_| \verb|[+voice]| \verb|[+vowel]|\\\verb|[-glide]| $\to$ \verb|[-palletized]| /  \verb|_| \verb|[-back]|\\\textipa{w} $\to$ \textipa{v} / \verb|[+vowel]| \verb|_| \verb|[+vowel]|\\\verb|[ ]| $\to$ \verb|[+palletized]| /  \verb|_| \textipa{i}\\\textipa{o} $\to$ \textipa{i} /  \verb|_| \verb|[-vowel]|* \verb|[-vowel]| \#\\\textipa{l} $\to$ \textipa{w} /  \verb|_| \#

\emph{Latin:}\\\begin{longtable}{lll|l}\toprule
$\varnothing$ $+$stem$+$ \textipa{s} & $\varnothing$ $+$stem$+$ \textipa{is} & $\varnothing$ $+$stem$+$ \textipa{i:} & UR
\\ \midrule
\textipa{arks} & \textipa{arkis} &  --  &  -- \\
\textipa{duks} & \textipa{dukis} &  --  &  -- \\
\textipa{daps} & \textipa{dapis} &  --  &  -- \\
\textipa{re:ks} & \textipa{re:gis} &  --  &  -- \\
\textipa{falanks} & \textipa{falangis} &  --  &  -- \\
\textipa{filiks} & \textipa{filikis} &  --  &  -- \\
\textipa{lapis} & \textipa{lapidis} &  --  &  -- \\
\textipa{li:s} & \textipa{li:tis} &  --  &  -- \\
\textipa{fraws} & \textipa{frawdis} &  --  &  -- \\
\textipa{noks} & \textipa{noktis} &  --  &  -- \\
\textipa{frons} & \textipa{frontis} &  --  &  -- \\
\textipa{frons} & \textipa{frondis} &  --  &  -- \\
\textipa{inku:s} & \textipa{inku:dis} &  --  &  -- \\
\textipa{sors} & \textipa{sortis} &  --  &  -- \\
\textipa{fu:r} & \textipa{fu:ris} &  --  &  -- \\
\textipa{murmur} & \textipa{murmuris} &  --  &  -- \\
\textipa{augur} & \textipa{auguris} &  --  &  -- \\
\textipa{arbor} & \textipa{arboris} &  --  &  -- \\
\textipa{pugil} & \textipa{pugilis} &  --  &  -- \\
\textipa{sal} & \textipa{salis} &  --  &  -- \\
\textipa{adeps} & \textipa{adipis} &  --  &  -- \\
\textipa{apeks} & \textipa{apikis} &  --  &  -- \\
\textipa{pri:nkeps} & \textipa{pri:nkipis} &  --  &  -- \\
\textipa{ekwes} & \textipa{ekwitis} &  --  &  -- \\
\textipa{miles} & \textipa{militis} &  --  &  -- \\
\textipa{no:men} & \textipa{no:minis} &  --  &  -- \\
\textipa{karmen} & \textipa{karminis} &  --  &  -- \\
\textipa{lu:men} & \textipa{lu:minis} &  --  &  -- \\
\textipa{wenter} & \textipa{wentris} &  --  &  -- \\
\textipa{pater} & \textipa{patris} &  --  &  -- \\
\textipa{kada:wer} & \textipa{kada:weris} &  --  &  -- \\
\textipa{tu:ber} & \textipa{tu:beris} &  --  &  -- \\
\textipa{piper} & \textipa{piperis} &  --  &  -- \\
\textipa{karker} & \textipa{karkeris} &  --  &  -- \\
\textipa{die:s} &  --  & \textipa{die:i:} &  -- \\
\textipa{li:ber} &  --  & \textipa{li:beri:} &  -- \\
\textipa{miser} &  --  & \textipa{miseri:} &  -- \\
\textipa{ager} &  --  & \textipa{agri:} &  -- \\
\textipa{sinister} &  --  & \textipa{sinistri:} &  -- \\
\textipa{liber} &  --  & \textipa{libri:} &  -- \\
\textipa{as} & \textipa{assis} &  --  &  -- \\
\textipa{os} & \textipa{ossis} &  --  &  -- \\
\textipa{far} & \textipa{farris} &  --  &  -- \\
\textipa{mel} & \textipa{mellis} &  --  &  -- \\
\textipa{o:s} & \textipa{o:ris} &  --  &  -- \\
\textipa{flo:s} & \textipa{flo:ris} &  --  &  -- \\
\textipa{mu:s} & \textipa{mu:ris} &  --  &  -- \\
\textipa{cru:s} & \textipa{cru:ris} &  --  &  -- \\
\textipa{kinis} & \textipa{kineris} &  --  &  -- \\
\textipa{pulvis} & \textipa{pulveris} &  --  &  -- \\
\bottomrule\end{longtable}
\begin{tabular}{l}\emph{Rules: }\\
\verb|[-sonorant]| $\to$ \verb|[-voice]| /  \verb|_| \verb|[-voice]|\\\textipa{e} $\to$ $2$ /  \verb|_| \verb|[-liquid]| \verb|[+vowel]|\\\verb|[-vowel]| $\to$ $\varnothing$ / \verb|[+coronal]| \verb|_| \#\\\verb|[-sonorant]| $\to$ \textipa{s} /  \verb|_| \#\\$\varnothing$ $\to$ \textipa{e} / \verb|[-sonorant]| \verb|_| \verb|[+voice]| \#\\$\varnothing$ $\to$ $2$ / \verb|[+sibilant]| \verb|_| \verb|[+vowel]| \verb|[-voice]|\\$\varnothing$ $\to$ $1$ / \# \verb|[-coronal]| \verb|[-high]| \verb|_| \verb|[+voice]| \textipa{i}
\end{tabular}
